went to clubs and pages instead of finances
found finances page
logged in - kinda surprised
Need to set up maillog - we had it setup but we don't want other people to need to have it setup

changed "expense" to yellow - maybe not our issue? LOL

wrapped finances route in a sign in page but it should not be gated behind

would like to drag receipts to upload box

Should indicate that purchase notes are required instead of pre-submission checklist

"clear image" should have a preview of image to check if image is actually clear

All details are currently defaulted
would like to zoom in more

Needs to be quick

Should throw him back to the top of the page to see the confirmation
    Even better to have the confirmation at the bottom.

NEXT TASK: VIEW RECEIPT SUBMISSION

found receipt submission page

TASK: Accept reimbursement request as a club VP

#bug: members can automatically add themselves as VP of clubs...

FOund the pending club approval page
Rejected an expense 
Would it be good to have an undo button.

I think 

TASK: Accept reimbursement request as a MES VP

#bug: go to tab that is permission locked and send you back to current tab. The second time it works
#details tab gives a  personal info

Accepted reimbursement request as MES VP

#pending reimburseemnt in wrong tab 

TASK: check submitted reimbursement

updated club expenses. looks 

TASK: feedback
At a glance, he liked it.
buttons are nice.
what happens when theres too many clubs? for MES VP
    maybe add a search filter to find clubs?
    quick navigation on the left organized alphabetically
    fuzzy searching? substring?
    accordion style dropdowns for clubs is nice
    Add charts as metrics?
        export function to csv excel.
    Add a total to see how much as currently be reimbursed
    add total to see how much MES has as a budget?
!!!! onboarding new clubs?