\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

We will demonstrate an end-to-end PoC of the MES Finance Platform that highlights risk-reducing functionality:
\begin{itemize}
  \item Intuitive web form for receipt submission
  \item Google Cloud Vision OCR on uploaded receipts
  \item LLM-based structured data extraction via Ollama (merchant, date, total)
  \item Full-stack flow: persist receipt image and parsed data, then render results in the Frontend UI
  \item Admin dashboard preview to show reimbursement request visibility
\end{itemize}

\noindent Demo flow:
\begin{enumerate}
  \item Upload a sample receipt image via the web UI
  \item OCR runs automatically and parsed fields are extracted by the LLM
  \item The user reviews extracted data and submits the request
  \item The admin view shows the new request with key fields populated
\end{enumerate}

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Justin & 2\\
Zhenia & 2\\
Name 3 & Num\\
Name 4 & Num\\
Name 5 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\noindent \textbf{Supervisor's Name: } [fill in this information]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Justin & 2\\
Zhenia & 3\\
Name 3 & Num\\
Name 4 & Num\\
Name 5 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

There were 2 official team meetings, and 1 unofficial meeting, in which Luke (our supervisor) joined on the fly as we were having a separate meeting with the MES developers.


\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo. You can find the number of lectures in the time period of
interest by looking at the
\href{https://calendar.google.com/calendar/u/0/embed?src=rnboqiaki1k2la7rpu3bn0um58@group.calendar.google.com&ctz=America/Toronto}
{Google calendar} for the capstone course.}

\wss{NOTE: There will be approximately 13 lectures between the start of class
and the POC demos}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 13\\
Justin & 5\\
Zhenia & 4\\
Name 3 & Num\\
Name 4 & Num\\
Name 5 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\noindent \textbf{TA's Name: } Luke Schuurman (capstone@macengsociety.ca)

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 4\\
Justin & 4\\
Name 2 & Num\\
Name 3 & Num\\
Name 4 & Num\\
Name 5 & Num\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 90 & 100\% \\
Justin & 18 & 20\% \\
Name 2 & Num & \% \\
Name 3 & Num & \% \\
Name 4 & Num & \% \\
Name 5 & Num & \% \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Justin & 8 & 0 \\
Name 2 & Num & Num \\
Name 3 & Num & Num \\
Name 4 & Num & Num \\
Name 5 & Num & Num \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{CICD}

CICD has been used in the following ways in our project:
\begin{itemize}
    \item Automatic updates to our PDFs (build LaTeX documents on push/PR)
    \item Frontend linting and unit tests on push/PR
    \item Preview deployments for feature branches to support rapid review
\end{itemize}

\wss{Say how CICD will be used in your project}

\section{Team Charter Trigger Items}

Our triggers are based around communication, responsibilities, and scheduling.
\begin{itemize}
  \item Communication
    \begin{itemize}
      \item Use pull requests for code changes
      \item Discord for quick coordination
      \item Email for formal stakeholder communication
      \item Use GitHub issues for task management
    \end{itemize}
  \item Responsibilities
    \begin{itemize}
      \item Each member is responsible for their assigned issues
      \item Members are responsible for attending meetings
      \item Team roles (PM, Dev lead, etc.) rotate and are shared
    \end{itemize}
  \item Scheduling
    \begin{itemize}
      \item Issues are assigned with realistic deadlines
      \item Deadlines are met
    \end{itemize}
\end{itemize}

Violated triggers
\begin{itemize}
  \item Communication
    \begin{itemize}
      \item GitHub issues were not consistently used
    \end{itemize}
  \item Responsibilities
    \begin{itemize}
      \item N/A
    \end{itemize}
  \item Scheduling
    \begin{itemize}
      \item N/A
    \end{itemize}
\end{itemize}

To address the issue tracking gap, we will reinforce using GitHub issues for all tasks and review adherence in the next team meeting.


\wss{Provide a summary of the quantified triggers identified in the team's
charter.}

\wss{Provide a list of any violations of the triggers.  If the team wishes, the
violations can be summarized on aggregate, instead of naming specific team
members.}

\wss{Provide a plan to address the violations.  This could include revising the
triggers, if they are found to be too weak, strong or ambiguous.}

\section{Additional Productivity Metrics}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}