\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\\
\wss{The intention of the VnV plan is to increase confidence in the software.
However, this does not mean listing every verification and validation technique
that has ever been devised.  The VnV plan should also be a \textbf{feasible}
plan. Execution of the plan should be possible with the time and team available.
If the full plan cannot be completed during the time available, it can either be
modified to ``fake it'', or a better solution is to add a section describing
what work has been completed and what work is still planned for the future.}

\wss{The VnV plan is typically started after the requirements stage, but before
the design stage.  This means that the sections related to unit testing cannot
initially be completed.  The sections will be filled in after the design stage
is complete.  the final version of the VnV plan should have all sections filled
in.}

\newpage

\tableofcontents

\listoftables
\wss{Remove this section if it isn't needed}

\listoffigures
\wss{Remove this section if it isn't needed}

\newpage

\section{Symbols, Abbreviations, and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  BUC & Business Use Cases\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations, or acronyms --- you can simply reference the SRS
  \citep{SRS} tables, if appropriate}

\wss{Remove this section if it isn't needed}

\newpage

\pagenumbering{arabic}

This document ... \wss{provide an introductory blurb and roadmap of the
  Verification and Validation plan}

\section{General Information}

\subsection{Summary}

\wss{Say what software is being tested.  Give its name and a brief overview of
  its general functions.}

The MES Finance Tracking Platform is a web application that centralizes club reimbursement submissions, 
reviews, and approvals for the MES with role based access and receipt storage. The front end user interface 
will be tested for usability and functionality to ensure a smooth user experience. The back end data storage
will be tested for data integrity and security to ensure sensitive financial information is protected. The database
will be tested for performance and reliability to ensure quick access to financial records. 

\subsection{Objectives}

\wss{State what is intended to be accomplished.  The objective will be around
  the qualities that are most important for your project.  You might have
  something like: ``build confidence in the software correctness,''
  ``demonstrate adequate usability.'' etc.  You won't list all of the qualities,
  just those that are most important.}

\wss{You should also list the objectives that are out of scope.  You don't have 
the resources to do everything, so what will you be leaving out.  For instance, 
if you are not going to verify the quality of usability, state this.  It is also 
worthwhile to justify why the objectives are left out.}

\wss{The objectives are important because they highlight that you are aware of 
limitations in your resources for verification and validation.  You can't do everything, 
so what are you going to prioritize?  As an example, if your system depends on an 
external library, you can explicitly state that you will assume that external library 
has already been verified by its implementation team.}

\noindent In Scope Objectives:
\begin{itemize}
  \item Demonstrate software correctness of end-to-end user interface reimbursement workflow
  \item Ensure data integrity and security of sensitive financial information 
  \item Meet all performance/capacity targets for database access times
  \item Ensure financial accuracy of reimbursement camera captures and calculations
\end{itemize}

\noindent Out of Scope Objectives:
\begin{itemize}
  \item Comprehensive usability testing for all potential user personas due to limited resources.
\end{itemize}


\subsection{Extras}

\wss{Summarize the extras (if any) that were tackled by this project.  Extras
can include usability testing, code walkthroughs, user documentation, formal
proof, GenderMag personas, Design Thinking, etc.  Extras should have already
been approved by the course instructor as included in your problem statement.
You can use a pull request to update your extras (in TeamComposition.csv or
Repos.csv) if your plan changes as a result of the VnV planning exercise.}

N/A 

\subsection{Relevant Documentation}

\wss{Reference relevant documentation.  This will definitely include your SRS
  and your other project documents (design documents, like MG, MIS, etc).  You
  can include these even before they are written, since by the time the project
  is done, they will be written.  You can create BibTeX entries for your
  documents and within those entries include a hyperlink to the documents.}

% \citet{SRS}
\begin{itemize}
  \item SRS Documentation
    \begin{itemize}
      \item The SRS is the formal documentation of the functional and non-functional requirements for the project.
      All requirements that must be verified and validated are specified and elaborated on in the SRS.
    \end{itemize}
  \item Hazard Analysis Documentation
    \begin{itemize}
      \item Due to the project's nature of processing and storing financial data, many non-functional requirements 
      arise from hazards related to the security and integrity of data handling. Previously discovered hazards can also inform
      caution points during the verification and validation processes.
    \end{itemize}
  \item Problem Statement and Goals Documentation
    \begin{itemize}
      \item Validation of the requirements proposed in the SRS must relate to the overall goals of the project. The \textit{Problem Statement
      and Goals} documentation includes these high-level goals of the project, and is the primary source of information when the client and/or
      supervisors cannot be reached for clarification. 
    \end{itemize}
  \item Development Plan Documentation
    \begin{itemize}
      \item The development process is to achieve the goals and meet the requirements of the project. In the case that any requirements
      are later invalidated, the plans for development must be modified correspondingly. 
    \end{itemize}
  \item Design Documentation
    \begin{itemize}
      \item The software must be designed such that it meets the verification methods outlined in the VnV. For requirements that can be
      unit-tested, specifics will be included in the unit testing documentation. Many qualitative requirements, however, must be manually
      evaluated according to the procedures set forth in this document.
    \end{itemize}
  \item Unit Testing Plan Documentation
    \begin{itemize}
      \item The \textit{Unit Testing Plan} documentation will be required to reference the VnV Plan for outlined procedures for automatic
      tests, where applicable.
    \end{itemize}
\end{itemize}


\wss{Don't just list the other documents.  You should explain why they are relevant and 
how they relate to your VnV efforts.}

\section{Plan}

\wss{Introduce this section.  You can provide a roadmap of the sections to
  come.}

\subsection{Verification and Validation Team}

\noindent
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{3.5cm} >{\raggedright\arraybackslash}p{3.5cm} X}
\toprule
\textbf{Name} & \textbf{Role} & \textbf{Responsibilities}\\
\midrule
Thomas, Justin, Zhenia, Michael, Johnny & Member of MES Finance Tracker Development Team & Development, correctness and usability testing.\\
Luke & Capstone Project Supervisor & Outline all requirements and ensure all requirements have been met and considered.\\
Member of MES Finance Team & Stakeholder & Provide feedback on usability and correctness of financial calculations.\\
Member of MES Clubs & Stakeholder & Provide feedback on usability and correctness of reimbursement workflow.\\
\bottomrule
\end{tabularx}

\subsection{SRS Verification}

\wss{List any approaches you intend to use for SRS verification.  This may
  include ad hoc feedback from reviewers, like your classmates (like your
  primary reviewer), or you may plan for something more rigorous/systematic.}

\wss{If you have a supervisor for the project, you shouldn't just say they will
read over the SRS.  You should explain your structured approach to the review.
Will you have a meeting?  What will you present?  What questions will you ask?
Will you give them instructions for a task-based inspection?  Will you use your
issue tracker?}

\wss{Maybe create an SRS checklist?}

\noindent\textbf{Formal SRS Inspection} \\
\noindent\textbf{Individuals Involved:} Team Members, Luke (Supervisor) \\
\noindent\textbf{Inputs:} SRS Document and Checklist of Requirements and BUC \\
\noindent\textbf{Procedure:}
\begin{enumerate}
  \item Pre-read: all reviewers must read, annotate the SRS documentation, and prepare list of any questions and concerns.
  \item Meeting Walkthrough: reviewers meet to discuss if all requirements listed within the SRS are \emph{clear, verifiable, traceable} and have been met.
  They will also discuss if each BUC has been captured completely and accurately.
  \item Log defects, classify (major/minor), assign owners.
  \item Re-review and redo the process; sign-off when exit criteria are met.
\end{enumerate}
\noindent\textbf{End Criteria:} All major defects resolved; each requirement marked \emph{clear, verifiable, traceable}. \\
\noindent\textbf{Outputs:} Logged defects with resolutions; signed-off SRS document verification. \\


\subsection{Design Verification}

\wss{Plans for design verification}

\wss{The review will include reviews by your classmates}

\wss{Create a checklists?}

\noindent\textbf{Task-Based Validation with Stakeholders} \\
\noindent\textbf{Individuals Involved:} Team Members, MES Finance Team, Club Executives \\
\noindent\textbf{Inputs:} SRS Document and Checklist of Requirements and BUC, Each Stakeholder will provide list of desired functionality from the application \\
\noindent\textbf{Procedure:}
\begin{enumerate}
  \item Pre-read: all team members must review stakeholder desired functionality list and list questions or concerns where applicable.
  \item Meeting Walkthrough: reviewers meet to discuss with each individual stakeholder to see if requirements have been met.
  They will also discuss if each BUC has been captured completely, accurately, and is satisfactory compared to their initial list.
  \item Log defects, classify (major/minor), assign owners.
  \item Re-review and redo the process; sign-off when exit criteria are met.
\end{enumerate}
\noindent\textbf{End Criteria:} All stakeholders are satisfied with the apps functionality and each requirement marked \emph{clear, verifiable, traceable}. \\
\noindent\textbf{Outputs:} Logged defects with resolutions; signed-off SRS document verification. 

\noindent\textbf{Checklist to be Used for Design Verification} \\
\begin{itemize}
  \item Pages use consistent layout and design
  \item Buttons and links look clickable, disabled and hover states are differentiated
  \item Forms are easy to understand and fill out, with clear labels, units/currencies, and instructions
  \item Important actions are visually prominent
  \item Empty states explain what to do next
  \item Member can submit reimbursement with all required fields and receipt uploads
  \item File uploads only accept allowable types/sizes; oversized files return error message
  \item Reviewers can open request, see all details, and Approve/Reject with comments 
  \item Notifications are sent/shown at the correct times (upon submission and decision)
  \item Members can see their own requests and current statuses easily 
  \item Amounts always show 2 decimal points and use the correct currency symbol
  \item Dates and times are clearly outlined 
  \item Each role can only access their permitted features, information, and actions
  \item Approved requests are unable to be edited or resubmitted
  \item Sensitive pages require login, and sessions time out after period of inactivity
  \item Admin features are simple and hard to misuse
  \item Backups/restore plan exists and receipts are included
\end{itemize}

\subsection{Verification and Validation Plan Verification}

\wss{The verification and validation plan is an artifact that should also be
verified.  Techniques for this include review and mutation testing.}

\wss{The review will include reviews by your classmates}

\wss{Create a checklists?}

\noindent\textbf{Objective: }
Ensure that the V\&V Plan accurately defines all verification and validation
activities, aligns with the SRS and design documentation, and includes
measurable procedures for system and unit testing.

\noindent\textbf{Individuals Involved: } Team Members, Luke (Supervisor), Peer Reviewers

\noindent\textbf{Inputs: } Current version of the V\&V Plan, SRS, Design, and Unit Testing documents

\noindent\textbf{Procedure: }
\begin{enumerate}
  \item All reviewers read and annotate the plan, marking unclear, inconsistent, or incomplete sections.
  \item The team presents the plan to peers and the supervisor, who assess completeness, coverage, and clarity.
  \item Reviewers confirm that all required sections (team roles, verification methods, validation methods, test case traceability, and schedules) are properly included and justified.
  \item Any missing or unclear items are documented, categorized (minor/major), and assigned for correction.
  \item The plan is updated and re-evaluated until all checklist items are satisfied.
\end{enumerate}

\noindent\textbf{Exit Criteria: } all major issues have been resolved, every section meets consistency and completeness standards, plan is reviewed by supervisor.

\noindent\textbf{Outputs: } Review log containing identified issues and resolutions and final version version of the V\&V Plan.

\noindent\textbf{Verification Checklist:}

\begin{itemize}
  \item All sections of the V\&V Plan are present and clearly labeled.
  \item Objectives and scope are clearly defined and align with the SRS.
  \item Verification and validation methods are feasible and well justified.
  \item Roles and responsibilities of team members are specified.
  \item Traceability between requirements, design, and test cases is clear.
  \item Testing procedures and success criteria are measurable and realistic.
  \item Inputs, outputs, and review artifacts are well defined.
  \item Peer and supervisor review process is documented.
  \item Formatting, consistency, and terminology conform to standards.
  \item All identified issues or inconsistencies have been resolved.
\end{itemize}

\subsection{Implementation Verification}

\wss{You should at least point to the tests listed in this document and the unit
  testing plan.}

\wss{In this section you would also give any details of any plans for static
  verification of the implementation.  Potential techniques include code
  walkthroughs, code inspection, static analyzers, etc.}

\wss{The final class presentation in CAS 741 could be used as a code walkthrough.  There is also a possibility of using the final presentation (in CAS741) for a partial usability survey.}

\noindent\textbf{Objective:}
Ensure the correctness, quality, and maintainability of the codebase and its compliance with requirements through systematic testing and review.

\noindent\textbf{Relation to Other Documents:} The system-level tests described in this document validate the integrated behavior of the MES Finance Tracking Platform, while the unit-level tests verify the correctness of individual components and modules.

\noindent\textbf{Verification Activities:}
\begin{enumerate}
  \item \textbf{Code Walkthroughs:} Conducted bi-weekly among developers to ensure code readability, adherence to the design specification, and appropriate documentation.
  Each walkthrough focuses on newly implemented modules or functions to confirm alignment with the Module Interface Specification (MIS).
  
  \item \textbf{Code Inspections:} Performed at key development milestones. Each inspection evaluates code clarity, conformance to coding standards, naming conventions,
  and consistency across modules. Defects and deviations are logged and resolved prior to integration.
  
  \item \textbf{Static Analysis:} Automated static analyzers (e.g., \texttt{ESLint} for JavaScript / TypeScript) will be used to detect syntax errors, potential vulnerabilities, and code smells. Additional tools such as \texttt{Prettier} will enforce formatting consistency. Code quality metrics, including cyclomatic complexity and unused dependency checks, will be collected to ensure maintainability.
  
  \item \textbf{Unit Testing:} Each module will undergo automated testing with a minimum of 80\% code coverage. Unit tests verify logical correctness, handle boundary conditions, and confirm expected output against defined input cases.
  
  \item \textbf{Integration Verification:} Conducted after all modules pass their unit tests. Integration testing ensures modules interface correctly and data flows as defined in the MIS. Errors detected during integration will be logged and traced back to responsible modules.
  
  \item \textbf{System and Acceptance Testing:} System tests validate the complete software against functional and nonfunctional requirements. Stakeholder User Acceptance Testing (UAT) will confirm that the application meets all acceptance criteria.
\end{enumerate}

\noindent\textbf{Inputs:}
\begin{itemize}
  \item Implementation codebase and supporting libraries
  \item Unit testing plan and results
  \item Static analysis reports and linting logs
  \item Integration and system test reports
  \item MIS and design documentation
\end{itemize}

\noindent\textbf{Outputs:}
\begin{itemize}
  \item Verified implementation source code
  \item Code inspection and walkthrough reports
  \item Static analysis summaries and coverage metrics
  \item Approved unit, integration, and system test results
\end{itemize}

\noindent\textbf{End Criteria:}
\begin{itemize}
  \item All modules pass unit and integration tests without critical defects.
  \item Static analysis yields no unresolved warnings or high-severity vulnerabilities.
  \item Implementation verified to meet all functional and nonfunctional requirements.
  \item Supervisor and stakeholders approve code quality and testing outcomes.
\end{itemize}


\subsection{Automated Testing and Verification Tools}

The active automation stack in the MES Website App Router repository is based on
TypeScript/Next.js tooling and is currently focused on static checks plus a
small Jest suite. Since the finance prototype is still evolving rapidly and
depends on newer integrations (OCR and LLM-assisted extraction), the project is
using a manual-first verification strategy for finance workflows while gradually
expanding automation.

\noindent\textbf{Currently implemented automated checks:}
\begin{itemize}
  \item \textbf{Linting:} ESLint (strict mode via \texttt{pnpm run lint:strict}).
  \item \textbf{Formatting:} Prettier format checks (\texttt{pnpm run format:check}).
  \item \textbf{Type safety:} TypeScript no-emit checks (\texttt{pnpm run typecheck}).
  \item \textbf{Unit tests:} Jest with Next.js integration (\texttt{pnpm run test}).
  \item \textbf{CI pipeline:} GitHub Actions runs lint, typecheck, format-check, and Jest on push/PR.
\end{itemize}

\noindent\textbf{Current automated test scope:}
\begin{itemize}
  \item Existing Jest tests are present but limited in number and are currently concentrated in non-finance areas.
  \item No Playwright/Cypress/Vitest configuration is currently present in the repository.
  \item Jest coverage thresholds are not yet enforced in the current configuration.
\end{itemize}

\noindent\textbf{Finance-focused support for efficient testing:}
\begin{itemize}
  \item The receipt extraction API includes a \texttt{debug=true} mode for controlled testing without live OCR/LLM dependencies.
  \item Manual end-to-end checks under \texttt{pnpm dev} remain the primary finance verification path for this phase.
\end{itemize}

\noindent\textbf{Near-term automation expansion plan:}
\begin{itemize}
  \item Add Jest tests for finance-critical logic (authorization checks, status transitions, receipt validation boundaries).
  \item Add targeted API-route tests for approve/reject flows and finance authorization outcomes.
  \item Introduce test coverage reporting and thresholds after workflow behavior stabilizes.
\end{itemize}

\subsection{Software Validation}

\wss{If there is any external data that can be used for validation, you should
  point to it here.  If there are no plans for validation, you should state that
  here.}

\wss{You might want to use review sessions with the stakeholder to check that
the requirements document captures the right requirements.  Maybe task based
inspection?}

\wss{For those capstone teams with an external supervisor, the Rev 0 demo should 
be used as an opportunity to validate the requirements.  You should plan on 
demonstrating your project to your supervisor shortly after the scheduled Rev 0 demo.  
The feedback from your supervisor will be very useful for improving your project.}

\wss{For teams without an external supervisor, user testing can serve the same purpose 
as a Rev 0 demo for the supervisor.}

\wss{This section might reference back to the SRS verification section.}

\noindent\textbf{Stakeholder UAT Against Acceptance Criteria} \\
\noindent\textbf{Individuals Involved:} Team Members, MES Finance Team, Club Executives \\
\noindent\textbf{Points of Clarification:}
\begin{enumerate}
  \item Ensure all MES software acceptance criteria have been met and incorporated into the final product.
  \item Ensure application workflow meets the needs of club executives and MES finance team members.
  \item Ensure all performance and capacity targets have been met in terms of concurrent users, API response times, and database access times.
  \item Ensure all financial calculations and camera receipt captures are accurate and reliable.
  \item Ensure application is usable and intuitive for all intended user personas during Rev 0 demo
\end{enumerate}

\section{System Tests}

\wss{There should be text between all headings, even if it is just a roadmap of
the contents of the subsections.}

This section describes the planned system tests for verifying the MES Finance Tracking Platform. 
Each subsection corresponds to one or more functional requirements defined in the SRS.
 The goal is to ensure that all reimbursement-related workflows—submission, review, and status tracking—perform as intended.

\subsection{Tests for Functional Requirements}

\wss{Subsets of the tests may be in related, so this section is divided into
  different areas.  If there are no identifiable subsets for the tests, this
  level of document structure can be removed.}

\wss{Include a blurb here to explain why the subsections below
  cover the requirements.  References to the SRS would be good here.}

The following tests verify that the MES Finance Tracking Platform correctly implements the functional requirements defined in Section 9.1 of the SRS. 
These tests ensure that all features related to reimbursement submission, review, and audit logging behave as expected.

\subsubsection{Area of Testing — Reimbursement Submission}

This area covers \textbf{Functional Requirements FRQ-1} and \textbf{FRQ-4}, ensuring that club members can submit expense claims with attached digital receipts and that data is permanently stored.

\textbf{Title for Test:} Submit Expense Reimbursement Request \\
\textbf{Test-id:} FRQ-1-SUBMIT

\begin{itemize}
    \item \textbf{Control:} Manual versus Automatic \\
    Automatic (performed using UI automation with manual verification)
    \item \textbf{Initial State:} \\
    The user is logged in as a valid club member with an existing club ID. No reimbursement requests are currently active for that user.
    \item \textbf{Input:} \\
    Receipt file (PDF or image $\leq$10 MB), amount = \$100, reimbursement form fields completed.
    \item \textbf{Output (Expected Result):} \\
    The request appears in the user’s dashboard with status = ``Submitted.'' The uploaded receipt is stored and accessible under that request.
    \item \textbf{Test Case Derivation:} \\
    Based on BUC-2 (``Submitting Reimbursement Request'') and FRQ-1/FRQ-4 in the SRS. Confirms form submission, file upload, and database persistence.
    \item \textbf{How Test Will Be Performed:} \\
    Using Cypress or Playwright to automate UI submission, then verifying MongoDB entries and front-end confirmation.
\end{itemize}

\subsubsection{Area of Testing — Reimbursement Review Workflow}

This area verifies \textbf{FRQ-2}, \textbf{FRQ-3}, and \textbf{FRQ-5}, ensuring that MES reviewers can view submissions, approve/reject them, and that actions are recorded in the audit trail.

\textbf{Title for Test:} Review and Approve Reimbursement Request \\
\textbf{Test-id:} FRQ-2-REVIEW

\begin{itemize}
    \item \textbf{Control:} Manual versus Automatic \\
    Semi-automatic (UI actions by MES reviewer, back-end verification automated)
    \item \textbf{Initial State:} \\
    A reimbursement request exists in ``Submitted'' status. MES reviewer is logged in with admin privileges.
    \item \textbf{Input:} \\
    Reviewer selects request $\rightarrow$ clicks ``Approve'' $\rightarrow$ enters approval note.
    \item \textbf{Output (Expected Result):} \\
    Request status = ``Approved.'' Submitter is notified. Audit log records: \{timestamp, reviewerID, action: Approved\}.
    \item \textbf{Test Case Derivation:} \\
    Based on BUC-3 (``Reviewing Reimbursement Request'') and FRQ-2/FRQ-5 in the SRS.
    \item \textbf{How Test Will Be Performed:} \\
    UI interaction test plus backend log verification using database queries to ensure audit trail persistence.
\end{itemize}

\subsubsection{Area of Testing — Reimbursement Status Tracking}

This test verifies \textbf{FRQ-3} and \textbf{FRQ-6}, ensuring that submitters and authorized users can view real-time reimbursement statuses.

\textbf{Title for Test:} View Reimbursement Status \\
\textbf{Test-id:} FRQ-3-STATUS

\begin{itemize}
    \item \textbf{Control:} Manual versus Automatic \\
    Automatic (API and UI check)
    \item \textbf{Initial State:} \\
    Multiple reimbursement requests exist with different statuses (submitted, under review, approved).
    \item \textbf{Input:} \\
    User navigates to the ``My Requests'' page or queries the API endpoint \texttt{/api/reimbursements}.
    \item \textbf{Output (Expected Result):} \\
    The UI displays the correct status for each request. The API returns accurate data matching the database state.
    \item \textbf{Test Case Derivation:} \\
    Derived from FRQ-3 and FRQ-6, validating that access is role-based and statuses are synchronized with the database.
    \item \textbf{How Test Will Be Performed:} \\
    Automated API tests (Postman/pytest) and front-end UI verification to cross-validate consistency.
\end{itemize}

\subsubsection{Area of Testing — Receipt Persistence and Security}

This area validates the data integrity requirement from \textbf{FRQ-4} and \textbf{Security Requirements INT-1, PRI-1}.

\textbf{Title for Test:} Verify Receipt Storage Security \\
\textbf{Test-id:} FRQ-4-STORAGE

\begin{itemize}
    \item \textbf{Control:} Automatic
    \item \textbf{Initial State:} \\
    One reimbursement submission with a receipt attached.
    \item \textbf{Input:} \\
    Query the database and storage bucket for the receipt file.
    \item \textbf{Output (Expected Result):} \\
    Receipt file is encrypted at rest (per SRS Section 16.3), accessible only to authorized users, and retrievable without corruption.
    \item \textbf{Test Case Derivation:} \\
    From FRQ-4 and SRS Section 16 (INT, PRI).
    \item \textbf{How Test Will Be Performed:} \\
    Check encryption metadata and permissions via the cloud storage API (AWS S3 or Vercel storage).
\end{itemize}

\subsubsection{Area of Testing — Audit Logging}

This area ensures \textbf{FRQ-5} is satisfied by verifying audit log entries for all major actions.

\textbf{Title for Test:} Audit Log Verification \\
\textbf{Test-id:} FRQ-5-AUDIT

\begin{itemize}
    \item \textbf{Control:} Automatic
    \item \textbf{Initial State:} \\
    System contains multiple reimbursement records with various user actions.
    \item \textbf{Input:} \\
    Run log export query for ``Approve'' or ``Reject'' events.
    \item \textbf{Output (Expected Result):} \\
    Each event entry includes timestamp, userID, actionType, and status change. Logs persist for at least 3 years per SRS Section 16.4.
    \item \textbf{Test Case Derivation:} \\
    Derived from FRQ-5 and Audit Requirements [AUD-1, AUD-2].
    \item \textbf{How Test Will Be Performed:} \\
    Automated test script queries audit collection and validates schema and retention policies.
\end{itemize}


\subsection{Tests for Nonfunctional Requirements}

The following tests verify that the MES Finance Tracking Platform meets the nonfunctional requirements defined in the SRS. These include performance, usability, security, and maintainability tests to ensure the system is robust, efficient, and user-friendly.

\subsubsection{Area of Testing — Performance and Latency}

This area covers \textbf{Speed and Latency Requirements [SaL]} and partially overlaps with \textbf{Robustness or Fault-Tolerance Requirements [FLT]}.

\textbf{Title for Test:} API and Page Load Performance Test \\
\textbf{Test-id:} NFL-SAL-1

\begin{itemize}
    \item \textbf{Control:} Automatic
    \item \textbf{Initial State:} \\
    System deployed to staging environment with seeded database (100 clubs, 1,000 reimbursement requests).
    \item \textbf{Input:} \\
    Execute 100 concurrent API requests for reimbursement data and record response times. Load homepage and dashboard in Chrome using Lighthouse.
    \item \textbf{Output (Expected Result):} \\
    API response times average below 1 second; page load times under 3 seconds; file uploads ($<10$ MB) complete within 5 seconds.
    \item \textbf{Test Case Derivation:} \\
    Derived from SRS Section 13.1 [SaL-1, SaL-2, SaL-3].
    \item \textbf{How Test Will Be Performed:} \\
    Automated load testing with tools such as JMeter or Locust, combined with Lighthouse performance scoring. Results summarized in a table comparing observed times to SRS thresholds.
\end{itemize}

\subsubsection{Area of Testing — Usability and Accessibility}

This area validates \textbf{Ease of Use and Learning [EUL]}, \textbf{Accessibility [ABL]}, and \textbf{Style [STY]} requirements.

\textbf{Title for Test:} Usability and Accessibility Evaluation \\
\textbf{Test-id:} NFL-USAB-1

\begin{itemize}
    \item \textbf{Control:} Manual (survey-based)
    \item \textbf{Initial State:} \\
    A functioning system prototype accessible by 5 test users representing different roles (club member, executive, MES reviewer).
    \item \textbf{Input:} \\
    Users perform typical tasks (submit reimbursement, review request, check status). Afterward, they complete a usability survey using a 5-point Likert scale.
    \item \textbf{Output (Expected Result):} \\
    Average ease-of-use rating $\geq$ 4/5. All UI components are keyboard-navigable and meet WCAG 2.1 AA color contrast.
    \item \textbf{Test Case Derivation:} \\
    Based on SRS Sections 11 and 12, especially [EUL-1] and [ABL-1 – ABL-5].
    \item \textbf{How Test Will Be Performed:} \\
    Observation-based usability session followed by survey analysis. Accessibility verified with automated tools (axe-core, Lighthouse accessibility audits).
\end{itemize}

\subsubsection{Area of Testing — Security and Privacy}

This area ensures compliance with \textbf{Access [ACS]}, \textbf{Integrity [INT]}, and \textbf{Privacy [PRI]} requirements.

\textbf{Title for Test:} Role-Based Access and Data Protection Test \\
\textbf{Test-id:} NFL-SEC-1

\begin{itemize}
    \item \textbf{Control:} Automatic with manual verification
    \item \textbf{Initial State:} \\
    Test users include a general member, club executive, and MES admin, each authenticated with proper roles.
    \item \textbf{Input:} \\
    Attempt unauthorized access to restricted endpoints (e.g., reviewing reimbursements as a non-admin). Submit tampered form payloads.
    \item \textbf{Output (Expected Result):} \\
    Unauthorized requests receive HTTP 403 responses; input validation prevents injection/XSS; all communication uses HTTPS (TLS 1.2+). Sensitive fields are encrypted in the database.
    \item \textbf{Test Case Derivation:} \\
    Derived from SRS Section 16: [ACS-1, INT-1, PRI-1].
    \item \textbf{How Test Will Be Performed:} \\
    Automated penetration testing with OWASP ZAP or Burp Suite; verification of encryption and RBAC through API inspection and code review.
\end{itemize}

\subsubsection{Area of Testing — Maintainability and Supportability}

This area validates \textbf{Maintenance [MNT]} and \textbf{Supportability [SUP]} requirements.

\textbf{Title for Test:} Code Quality and Documentation Compliance \\
\textbf{Test-id:} NFL-MNT-1

\begin{itemize}
    \item \textbf{Control:} Static test (manual review and CI enforcement)
    \item \textbf{Initial State:} \\
    Project repository set up with ESLint and Prettier configuration as specified in the SRS.
    \item \textbf{Input:} \\
    Run code through linting and formatting checks; review developer documentation for completeness.
    \item \textbf{Output (Expected Result):} \\
    No critical linting errors; documentation covers setup, deployment, and troubleshooting. All dependencies are updated to current minor versions.
    \item \textbf{Test Case Derivation:} \\
    Derived from SRS Section 15 [MNT-1, SUP-1, SUP-2].
    \item \textbf{How Test Will Be Performed:} \\
    CI pipeline enforces linting and formatting. Manual inspection ensures documentation matches environment setup and maintenance requirements.
\end{itemize}


\subsection{Traceability Between Test Cases and Requirements}

\wss{Provide a table that shows which test cases are supporting which
  requirements.}

  This table maps the high-level Functional Requirements to the supporting Non-Functional Requirements that must be considered during testing to ensure the system's overall quality, security, and performance.

\vspace{0.5cm}

\begin{longtable}{p{0.4\linewidth} p{0.55\linewidth}}
\caption{Traceability Matrix for MES Finance Tracking Platform} \\
\toprule
\textbf{Functional Requirement (FRQ)} & \textbf{Supporting Non-Functional Requirement IDs (NFR)} \\
\midrule
\endfirsthead
\toprule
\textbf{Functional Requirement (FRQ)} & \textbf{Supporting Non-Functional Requirement IDs (NFR)} \\
\midrule
\endhead
\bottomrule
\endfoot
\textbf{FRQ-1:} The system shall allow MES clubs and teams to submit expense claims. &
EUL-1, UaP-2, ABL-1, ABL-3, ABL-5, SaL-1, SaL-2, FLT-2, CAP-1, ACS-1, ACS-2, INT-1, PRI-1, PRI-2, AUD-1, CUL-1, SEI-2, AUL-1, STD-1, STD-2 \\
\midrule
\textbf{FRQ-2:} The system shall provide MES reviewers with tools to efficiently review, approve, or reject the reimbursement requests. &
APP-1, APP-2, STY-3, EUL-1, ABL-1, ABL-5, SaL-1, PRE-1, FLT-1, CAP-1, ACS-1, ACS-2, INT-1, PRI-1, PRI-2, AUD-1, AUD-2, CUL-1, SEI-2, AUL-1, AUL-2, STD-1, STD-2 \\
\midrule
\textbf{FRQ-3:} The system shall track the status of each expense claim (e.g., submitted, under review, approved, rejected, reimbursed). &
APP-2, STY-3, ABL-1, SaL-1, SaL-2, FLT-3, CAP-2, EXT-2, LNG-2, ACS-1, ACS-2, PRI-1, AUD-1, AUD-2, SEI-2, AUL-2, STD-1 \\
\midrule
\textbf{FRQ-4:} The system shall permanently store and retain digital receipt submissions. &
SaL-3, PRE-1, FLT-2, CAP-2, LNG-1, PRI-1, PRI-2, AUD-2, SEI-1, SEI-2, SEI-3, AUL-2, RDL-1, STD-1 \\
\midrule
\textbf{FRQ-5:} The system shall maintain an audit trail that records who submitted, reviewed, approved, or denied each expense claim. &
FLT-2, CAP-2, LNG-1, ACS-2, PRI-2, AUD-1, AUD-2, IMM-1, SEI-2, SEI-3, AUL-1, AUL-2, RDL-1, STD-1, STD-3 \\
\midrule
\textbf{FRQ-6:} The system shall enable access to club expense submissions to the submitters, and other club members with a role greater or equal to that of the submitter, or MES administrators and approvers. &
APP-3, ABL-1, ABL-5, SaL-1, SaL-2, CAP-1, EXT-2, ACS-1, ACS-2, INT-1, PRI-1, PRI-2, AUD-1, SEI-2, AUL-1, AUL-2, STD-1, STD-2 \\
\bottomrule
\end{longtable}

\subsection*{Legend: Non-Functional Requirement Categories}
\begin{itemize}
    \item \textbf{APP / STY:} Look and Feel Requirements (Appearance, Style)
    \item \textbf{EUL / UaP / ABL:} Usability and Humanity Requirements (Ease of Use, Understandability, Accessibility)
    \item \textbf{SaL / PRE / FLT / CAP / EXT / LNG:} Performance Requirements (Speed, Precision, Fault-Tolerance, Capacity, Extensibility, Longevity)
    \item \textbf{ACS / INT / PRI / AUD / IMM:} Security Requirements (Access, Integrity, Privacy, Audit, Immunity)
    \item \textbf{CUL:} Cultural Requirements
    \item \textbf{SEI / AUL / RDL / STD:} Compliance Requirements (Storage/Encryption/Infrastructure, Access/Audit/Logging, Retention/Disposal, Standards)
\end{itemize}

\noindent This matrix ensures that for every function the system performs, the corresponding quality attributes are verified through specific test cases.

\section{Unit Test Description}

This section defines module-level testing based on the MIS in
\textit{docs/Design/SoftDetailedDes/MIS.tex}. To reach a clear working production
prototype quickly, the team is using a manual-first testing strategy in the MES
monorepo staging branch environment by running \texttt{pnpm dev} and validating
module behavior continuously during development.

This approach is intentional for this phase: it maximizes iteration speed and
feedback turnaround while features are still changing quickly. Full automated
test infrastructure is deferred because the required setup is non-trivial for
newer integrations (including LLM/AI-assisted paths, external service
dependencies, secure secret handling, and deterministic test environments).

\subsection{Unit Testing Scope}

\noindent\textbf{In-scope modules for direct unit-level manual testing:}
\begin{itemize}
  \item \textbf{M2 - User Interface Module}: highest churn and highest user-facing defect risk.
  \item \textbf{M3 - Request Handler Module}: core workflow and state transitions.
  \item \textbf{M4 - Receipt Processing Module}: file acceptance, validation, and access controls.
  \item \textbf{M6 - Authentication Module}: session and authorization correctness.
  \item \textbf{M8 - Audit Logging Module}: compliance-critical auditability and retention behavior.
\end{itemize}

\noindent\textbf{Lower-priority modules for direct unit-level testing in this phase:}
\begin{itemize}
  \item \textbf{M1 - Hardware Hiding Module}
  \item \textbf{M5 - Notification Module}
  \item \textbf{M7 - Data Model Module}
\end{itemize}

These modules are still verified indirectly through integration/system tests and
through behavior observed from in-scope modules that depend on them.

\subsection{Unit Testing Philosophy and Evidence Process}

Each manual unit test run follows a checklist and is logged in a shared defect
log for rerun tracking. This provides repeatability while preserving the speed
of manual iteration.

\noindent\textbf{Required fields per execution record:}
\begin{tabularx}{\textwidth}{p{3.0cm}X}
\toprule
\textbf{Field} & \textbf{Description} \\
\midrule
\texttt{testId} & Stable identifier for the test case (for example \texttt{UT-M3-04}). \\
\texttt{result} & Pass, Fail, or Blocked. \\
\texttt{environment} & Runtime context used for testing (staging branch, \texttt{pnpm dev}, database seed state). \\
\texttt{tester} & Team member who executed the test. \\
\texttt{issueLink} & Linked issue/bug ticket when failed; N/A when passed. \\
\texttt{rerunStatus} & Not rerun, rerun-pass, or rerun-fail. \\
\bottomrule
\end{tabularx}

\subsection{Automation Posture}

\begin{itemize}
  \item \textbf{Manual now, automate later:} manual execution is the primary strategy until prototype behavior stabilizes.
  \item \textbf{Automation start point:} after prototype stabilization and environment/tooling maturity in the MES monorepo.
  \item \textbf{Initial automation targets:} highest-regression workflows first: authentication, status transitions, and receipt validation.
\end{itemize}

\subsection{Tests for Functional Requirements}

\subsubsection{M2: User Interface Module}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UT-M2-01} (Role-aware dashboard rendering)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Seeded users exist for member, executive, and finance admin.\\
\textbf{Input:} Log in with each role and open dashboard pages.\\
\textbf{Output:} Each role only sees allowed actions and data panes.\\
\textbf{Test Case Derivation:} Derived from FRQ-6 and MIS M2 \texttt{renderDashboard}.\\
\textbf{How test will be performed:} Run \texttt{pnpm dev}, log in with role accounts, and compare visible actions against RBAC expectations.

\item \textbf{Test-id:} \texttt{UT-M2-02} (Form validation failure path)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Member user on reimbursement form page.\\
\textbf{Input:} Submit with missing required fields and invalid amount format.\\
\textbf{Output:} Submission blocked; field-level errors shown; no persistence triggered.\\
\textbf{Test Case Derivation:} Derived from MIS M2 \texttt{handleFormSubmit} validation behavior.\\
\textbf{How test will be performed:} Enter invalid data via UI and verify inline errors and absence of created request.

\item \textbf{Test-id:} \texttt{UT-M2-03} (Successful submit flow)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Member user with valid session and clean draft form.\\
\textbf{Input:} Submit fully valid request payload and attached receipt metadata.\\
\textbf{Output:} Confirmation shown, navigation outcome succeeds, request visible in dashboard.\\
\textbf{Test Case Derivation:} Derived from FRQ-1 and MIS M2 \texttt{handleFormSubmit}.\\
\textbf{How test will be performed:} Submit valid form under \texttt{pnpm dev} and verify dashboard state.

\end{enumerate}

\subsubsection{M3: Request Handler Module}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UT-M3-01} (Authorized request creation)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Executive user is authenticated; request data is valid.\\
\textbf{Input:} Trigger create request flow.\\
\textbf{Output:} RequestID generated; status initialized to submitted.\\
\textbf{Test Case Derivation:} Derived from FRQ-1 and MIS M3 \texttt{createRequest}.\\
\textbf{How test will be performed:} Execute create flow and verify stored record attributes.

\item \textbf{Test-id:} \texttt{UT-M3-02} (Unauthorized request creation denied)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Non-executive user is authenticated.\\
\textbf{Input:} Attempt create request action.\\
\textbf{Output:} Unauthorized path returned; no request created.\\
\textbf{Test Case Derivation:} Negative path for MIS M3 \texttt{createRequest}.\\
\textbf{How test will be performed:} Execute same creation path under non-authorized role.

\item \textbf{Test-id:} \texttt{UT-M3-03} (Valid status transition)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Existing request in submitted state and finance admin session.\\
\textbf{Input:} Update status submitted $\rightarrow$ approved.\\
\textbf{Output:} Transition accepted; status persisted; audit side effects present.\\
\textbf{Test Case Derivation:} Derived from FRQ-2, FRQ-3, FRQ-5 and MIS M3 \texttt{updateStatus}.\\
\textbf{How test will be performed:} Perform status update from reviewer UI and verify resulting state and logs.

\item \textbf{Test-id:} \texttt{UT-M3-04} (Invalid status transition rejected)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Existing request already approved.\\
\textbf{Input:} Attempt approved $\rightarrow$ submitted rollback transition.\\
\textbf{Output:} Invalid transition rejected; state unchanged.\\
\textbf{Test Case Derivation:} Negative path for MIS M3 transition policy.\\
\textbf{How test will be performed:} Attempt prohibited transition and verify immutable resulting state.

\end{enumerate}

\subsubsection{M4: Receipt Processing Module}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UT-M4-01} (Valid receipt upload accepted)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Authenticated user and editable reimbursement request.\\
\textbf{Input:} Upload valid PDF/image receipt under 10 MB.\\
\textbf{Output:} Receipt stored and linked to request with retrievable metadata.\\
\textbf{Test Case Derivation:} Derived from FRQ-4 and MIS M4 \texttt{uploadReceipt}.\\
\textbf{How test will be performed:} Upload file from form and verify attachment appears on request details.

\item \textbf{Test-id:} \texttt{UT-M4-02} (Invalid type/size rejected)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Authenticated user on upload flow.\\
\textbf{Input:} Upload unsupported MIME type and oversize file.\\
\textbf{Output:} File rejected with clear error; no persistence side effect.\\
\textbf{Test Case Derivation:} Negative path for MIS M4 \texttt{uploadReceipt}.\\
\textbf{How test will be performed:} Execute both invalid inputs and verify rejection behavior.

\item \textbf{Test-id:} \texttt{UT-M4-03} (Unauthorized receipt access denied)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Receipt exists for another club/request scope.\\
\textbf{Input:} Non-authorized user requests receipt link.\\
\textbf{Output:} Access denied; no signed URL returned.\\
\textbf{Test Case Derivation:} Negative path for MIS M4 \texttt{getReceiptLink}.\\
\textbf{How test will be performed:} Attempt cross-scope access under restricted role and verify denial.

\end{enumerate}

\subsubsection{M6: Authentication Module}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UT-M6-01} (Failed-auth lockout threshold)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Valid user account not locked.\\
\textbf{Input:} Repeated invalid credentials beyond max failed attempts.\\
\textbf{Output:} Account lockout triggered at configured threshold.\\
\textbf{Test Case Derivation:} Derived from ACS-1 and MIS M6 \texttt{authenticateUser}.\\
\textbf{How test will be performed:} Submit invalid login attempts and verify lockout behavior.

\item \textbf{Test-id:} \texttt{UT-M6-02} (Authorization allow/deny by role)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Session tokens for member and finance admin.\\
\textbf{Input:} Attempt protected action requiring finance admin privilege.\\
\textbf{Output:} Member denied, finance admin allowed.\\
\textbf{Test Case Derivation:} Derived from FRQ-6 and MIS M6 \texttt{verifyAuthorization}.\\
\textbf{How test will be performed:} Run action under both roles and compare decisions.

\end{enumerate}

\subsubsection{M8: Audit Logging Module}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UT-M8-01} (Log integrity and redaction)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Audit store available with redaction fields configured.\\
\textbf{Input:} Trigger an auditable approval action containing metadata with sensitive fields.\\
\textbf{Output:} Event stored with required fields and sensitive data redacted.\\
\textbf{Test Case Derivation:} Derived from FRQ-5, PRI-1, AUD-1, AUD-2 and MIS M8 \texttt{logAction}.\\
\textbf{How test will be performed:} Execute approval event and inspect resulting audit entry schema.

\item \textbf{Test-id:} \texttt{UT-M8-02} (Events by request query)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Request has multiple lifecycle events in the audit stream.\\
\textbf{Input:} Query events for specific request and time window.\\
\textbf{Output:} Ordered event sequence returned with expected request-scoped entries only.\\
\textbf{Test Case Derivation:} Derived from MIS M8 \texttt{getEventsByRequest}.\\
\textbf{How test will be performed:} Retrieve events and verify order, membership, and timestamps.

\item \textbf{Test-id:} \texttt{UT-M8-03} (Retention behavior)\\
\textbf{Type:} Functional, Dynamic, Manual\\
\textbf{Initial State:} Audit store contains events older than retention threshold in test dataset.\\
\textbf{Input:} Trigger retention cleanup operation.\\
\textbf{Output:} Expired entries archived/purged according to configured policy.\\
\textbf{Test Case Derivation:} Derived from AUD-2, RDL-1 and MIS M8 \texttt{purgeExpiredEvents}.\\
\textbf{How test will be performed:} Run cleanup flow and verify retained vs removed entries.

\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

\subsubsection{Module-level Nonfunctional Checks}

\begin{enumerate}

\item \textbf{Test-id:} \texttt{UNF-M2-01} (Usability and accessibility interaction)\\
\textbf{Type:} Nonfunctional, Dynamic, Manual\\
\textbf{Initial State:} Prototype running locally from \texttt{pnpm dev}.\\
\textbf{Input/Condition:} Keyboard-only navigation through dashboard, form, and status pages.\\
\textbf{Output/Result:} Core flows are keyboard navigable and understandable without external help.\\
\textbf{How test will be performed:} Walk through standard user tasks and record barriers in defect log.

\item \textbf{Test-id:} \texttt{UNF-M3-01} (Request handler responsiveness)\\
\textbf{Type:} Nonfunctional, Dynamic, Manual\\
\textbf{Initial State:} Seeded local/staging dataset with typical request volume.\\
\textbf{Input/Condition:} Execute create and update actions repeatedly during active dev session.\\
\textbf{Output/Result:} Actions complete within acceptable interactive latency and do not block workflow.\\
\textbf{How test will be performed:} Time-box repeated actions and record response lag observations.

\item \textbf{Test-id:} \texttt{UNF-M4-01} (Receipt upload performance)\\
\textbf{Type:} Nonfunctional, Dynamic, Manual\\
\textbf{Initial State:} Editable request with upload endpoint available.\\
\textbf{Input/Condition:} Upload representative files up to 10 MB.\\
\textbf{Output/Result:} Uploads complete within SRS latency expectations and return stable status feedback.\\
\textbf{How test will be performed:} Run repeated upload attempts and capture completion timing.

\item \textbf{Test-id:} \texttt{UNF-M6-01} (Session expiry and protected route enforcement)\\
\textbf{Type:} Nonfunctional, Security, Manual\\
\textbf{Initial State:} Authenticated session near/at expiry threshold.\\
\textbf{Input/Condition:} Access protected pages after session expires or token is invalidated.\\
\textbf{Output/Result:} Session is rejected and sensitive actions are blocked.\\
\textbf{How test will be performed:} Force expiry/invalidation and validate route protection behavior.

\item \textbf{Test-id:} \texttt{UNF-M8-01} (Audit retention and retrieval consistency)\\
\textbf{Type:} Nonfunctional, Compliance, Manual\\
\textbf{Initial State:} Audit dataset contains recent and aged records.\\
\textbf{Input/Condition:} Query and retention operations executed in sequence.\\
\textbf{Output/Result:} Retrieval remains consistent and retention policy is respected.\\
\textbf{How test will be performed:} Compare pre/post operation query results against expected policy outcomes.

\end{enumerate}

\subsection{Completion Criteria for Prototype Sign-off}

Prototype sign-off for this phase requires all in-scope module tests to be
executed at least once with no unresolved critical defects remaining in the
defect log. Any failed critical test must have a linked issue, a fix, and a
documented rerun result before sign-off.

\subsection{Traceability Between Test Cases and Modules}

\begin{longtable}{p{1.4cm} p{3.8cm} p{4.5cm} p{4.3cm}}
\caption{Unit Test Traceability Matrix (Module-Level)}\\
\toprule
\textbf{Module} & \textbf{Unit Test IDs} & \textbf{Primary MIS Access Programs} & \textbf{Related FRQ/NFR Coverage} \\
\midrule
\endfirsthead
\toprule
\textbf{Module} & \textbf{Unit Test IDs} & \textbf{Primary MIS Access Programs} & \textbf{Related FRQ/NFR Coverage} \\
\midrule
\endhead
\bottomrule
\endfoot
M2 & \texttt{UT-M2-01}, \texttt{UT-M2-02}, \texttt{UT-M2-03}, \texttt{UNF-M2-01}
& \texttt{renderDashboard}, \texttt{renderRequestForm}, \texttt{handleFormSubmit}
& FRQ-1, FRQ-3, FRQ-6; EUL-1, ABL-1, ABL-5, STY-3 \\
\midrule
M3 & \texttt{UT-M3-01}, \texttt{UT-M3-02}, \texttt{UT-M3-03}, \texttt{UT-M3-04}, \texttt{UNF-M3-01}
& \texttt{createRequest}, \texttt{getRequestDetails}, \texttt{updateStatus}
& FRQ-1, FRQ-2, FRQ-3, FRQ-5; SaL-1, FLT-1, ACS-2, AUD-1 \\
\midrule
M4 & \texttt{UT-M4-01}, \texttt{UT-M4-02}, \texttt{UT-M4-03}, \texttt{UNF-M4-01}
& \texttt{uploadReceipt}, \texttt{getReceiptLink}, \texttt{removeReceipt}
& FRQ-4; SaL-3, INT-1, PRI-1, PRI-2 \\
\midrule
M6 & \texttt{UT-M6-01}, \texttt{UT-M6-02}, \texttt{UNF-M6-01}
& \texttt{authenticateUser}, \texttt{verifyAuthorization}, \texttt{revokeSession}
& FRQ-6; ACS-1, ACS-2, INT-1, IMM-1 \\
\midrule
M8 & \texttt{UT-M8-01}, \texttt{UT-M8-02}, \texttt{UT-M8-03}, \texttt{UNF-M8-01}
& \texttt{logAction}, \texttt{getEventsByRequest}, \texttt{purgeExpiredEvents}
& FRQ-5; AUD-1, AUD-2, PRI-2, RDL-1, AUL-2 \\
\midrule
M1, M5, M7 & Indirect coverage in this phase (system and integration tests)
& Infrastructure abstraction, notification dispatch, and persistence internals
& Covered indirectly by in-scope module tests and end-to-end workflows \\
\end{longtable}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions?}
  \textbf{Ease of Use}
  \begin{enumerate}
      \item On a scale of 1--5, how easy was it to submit a reimbursement request with all required information and receipt uploads?
      \item How intuitive did you find the navigation between different sections of the platform (dashboard, submission form, request status)?
      \item Did you encounter any confusing terminology or unclear instructions while using the system?
  \end{enumerate}

  \textbf{Efficiency}
  \begin{enumerate}
      \item Approximately how long did it take you to complete your first reimbursement submission?
      \item Did the system provide adequate feedback during file uploads and form submission processes?
      \item Were you able to quickly locate and check the status of your previous reimbursement requests?
  \end{enumerate}

  \textbf{Role-Specific Functionality}
  \begin{itemize}
      \item \textbf{For Reviewers:} How easy was it to view all relevant details needed to approve or reject a reimbursement request?
      \item \textbf{For Club Members:} Did you feel confident that your submission was successful after completing the form?
      \item \textbf{For Admins:} How efficiently could you access and manage reimbursement data across multiple clubs?
  \end{itemize}

  \textbf{Accessibility and Design}
  \begin{enumerate}
      \item Were all buttons, links, and interactive elements clearly identifiable and easy to click/tap?
      \item Did the color contrast and text sizing make the interface comfortable to read?
      \item Were you able to complete all tasks using only your keyboard (without a mouse)?
  \end{enumerate}

  \textbf{Error Handling}
  \begin{enumerate}
      \item If you encountered any errors, were the error messages clear and helpful in resolving the issue?
      \item Did the system prevent you from making mistakes (e.g., uploading invalid file types, missing required fields)?
      \item How satisfied were you with the system's response when attempting actions you didn't have permission for?
  \end{enumerate}

  \textbf{Overall Satisfaction}
  \begin{enumerate}
      \item On a scale of 1--5, how likely are you to recommend this platform to other MES clubs?
      \item What feature or aspect of the platform did you find most helpful or well-designed?
      \item What improvements would you suggest to make the platform easier to use?
  \end{enumerate}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete the verification and validation of your project?
  Examples of possible knowledge and skills include dynamic testing knowledge,
  static testing knowledge, specific tool usage, Valgrind etc.  You should look to
  identify at least one item for each team member.
  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?
\end{enumerate}


\noindent\textbf{Thomas's Reflection:}
\begin{enumerate}
  \item Something that went well for this deliverable was the way that we were all able to split up the work.
  We each individually assigned ourselves a section to write but all came together to discuss the overall structure
  and flow of the document. We were able to complete the document on time and with good quality.
  \item A pain point that was experienced in this deliverable was ensuring that we were able to complete the deliverable
  in a timely manner while balancing other course work. We weren't really able to solve it for this week due to 
  the number of midterms and assignments from other courses, but we will try to plan better for future deliverables.
  \item One knowledge area that I will need to acquire to successfully complete the verification and validation is 
  how to perform dynamic testing for the front end UI framework and how to measure and report database access and API 
  response times. For me personally, I believe this is a skill that will be vital in completing the testing portion of 
  the project but it will also be a useful skill to have in my future career as a software engineer.
  \item For both knowledge areas, there is a structured method and a practical method of learning. The structured method
  involves using online resources, taking courses, or reading documentation to learn the concepts and theory behind the 
  topics. Meanwhile, the practical method involves hands-on experience by actually implementing tests and measuring performance
  on our project. The structured method can be used by all individuals within the group to build a foundation of understanding
  for how to perform the tests, while the practical method will be used by me to actually implement the tests and measure performance
  on our project. I believe that the practical method will be more effective for me as I learn best by trying and learning
  from my mistakes.
\end{enumerate}

\noindent\textbf{Justin's Reflection:}
\begin{enumerate}
  \item For this deliverable, something that went well was the we took initiative to take on work instead of handing out work deliberatly.
  This shows that we are all motivated to complete the deliverable and that we trust each other pick up work to share the workload. Its better than 
  how we previously handled work delegation because theres more autonomy and less micromanagement.
  \item A pain point was aligning out understanding of the deliverable structure and content. Even though we are relatively on the same page, specifics about the 
  requirements and content were inconsistent amongst group members. This caused isseus when deciding how we wanted to create test cases and what should be included. The main resolution
  involved having more discussions and clarifying our understanding of the deliverable requirements.
  \item To properly complete this project, we needed to learn different possible methods to perform dynamic testing for the front end UI framework and how to measure and report database access and API 
  response times. For me, there was a lack of knowledge on different technologies that would allow me to create automated test cases, which is essential for the testing portion of the project.
  \item To acquire the knowledge and skills needed, I want to take more time to find all the possible tools and technologies that can be applied to a situation, compared to just picking from the ones I already know.
  I can also try to learn from others who have more experience in testing and ask for their recommendations on what tools to use. I will most likely pursue the second option because I believe learning from others is more efficient and effective.
\end{enumerate}

\noindent\textbf{Zhenia's Reflection:}
\begin{enumerate}
  \item What went well was our team's ability to self-organize and take ownership of different sections without extensive coordination. This autonomous approach was more efficient than our previous deliverables and allowed us to complete the work on time.
  \item The main challenge was balancing specificity in test cases with our current level of implementation knowledge. I addressed this by focusing on clear inputs and expected outputs while maintaining flexibility for later refinement.
  \item I need to develop proficiency in end-to-end testing for our Next.js application, particularly testing workflows that span the frontend, API, and database layers.
  \item I'll pursue hands-on experimentation with Cypress or Playwright on our existing codebase, as I learn best through practical application rather than theoretical study.
\end{enumerate}

\noindent\textbf{Michael's Reflection:}
\begin{enumerate}
  \item Similiar to some of our previous deliverables, I think that a lot of the information required to complete the deliverable was already collected before we started working on the deliverable. 
  Although the documents were kind of designed to be completed in this order because of their dependencies on each other, it's good that the content we had previously written was meaningful enough to ease
  work on this deliverable.
  \item There was some uncertainty regarding some of what information is required for each section of the document; the rubric provides a very high-level overview statement, while I personally was lost on some of the acronyms and expected information.
  I suspect the lectures would have answered some of my questions, but through cross-referencing the pink advice text, past works, and discussing with group members, I think we were able to not spend too much time blocked by a lack of information.
  \item For sure a lot of testing knowledge across various subdomains and languages will need to be acquired. For myself, although I have some knowledge about setting up linters and custom scripts, I don't have any formal experience with running comprehensive
  unit testing suites. Developing the testing and software at the same time, or really any "test-driven" development is a skill I will have to acquire for this project.
  \item I think for me, the most practical approach will be to kind of learn the systems as I go through trial and error and online resources, without focusing too much on perfecting my understanding based on ideal theory. There's still a lot of work we will have to do alongside verification and
  validation, so I anticipate that spending time to go out of my way and learn the testing systems from top to bottom will be impractical. Instead, maybe letting team members that are more experienced plan out the systems, and then contributing through adding
  regular unit tests, running custom tests, etc, will give me a better intuitive understanding of testing. Another approach might be to communicate more with my team members and kind of learn from them in a tutor-like relationship. This approach would see me trying to bolster my understanding quickly
  early on, and then leverage the new knowledge and skills to be able to contribute broadly to the VnV process later on. To be honest, I think maybe I haven't laid two approaches that are selectable: I think that depending on the development situation and my teammates preferences,
  one of the approaches will naturally be the one I pursue.
\end{enumerate}

\noindent\textbf{Johnny's Reflection:}
\begin{enumerate}
  \item This deliverable felt relatively easier to write than the other ones. I think since we all have good software development experience (which includes testing), we were able to draw on our previous experiences to help us complete this deliverable.
  \item There were not many pain points I encountered while writing this deliverable. Some of the sections were a little confusing, but this was resolved within our meeting with our TA.
  \item Learning how to set up the entire testing suite will be something that we have learn. Our group members have experience working with testing tools in established codebases, but I think we lack the experience of actually setting up the testing tools from scratch.
  \item Two approaches I can use are (1) following official documentation/tutorials for each tool in a structured way, and (2) learning by implementing small tests directly in our project and reviewing them with teammates. I plan to use the second approach as my primary method because it gives immediate feedback in our real codebase, while still using documentation as a reference when I get stuck.
\end{enumerate}

\end{document}
