\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can reference the SRS tables if needed}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}

This section reports the evaluation of the functional requirements defined in the
SRS and tested through the system-level procedures introduced in the VnV Plan.
The evaluation focuses on the reimbursement workflow end-to-end: submission,
review and approval, status visibility, receipt persistence, and auditability.

\subsection{Evaluation Approach}

Functional validation was carried out using the planned test cases
\texttt{FRQ-1-SUBMIT}, \texttt{FRQ-2-REVIEW}, \texttt{FRQ-3-STATUS},
\texttt{FRQ-4-STORAGE}, and \texttt{FRQ-5-AUDIT}. Tests combined UI-driven
scenarios, API checks, and database/storage verification to ensure each
requirement was validated through observable behavior and persistent data state.

\subsection{Results Summary}

\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{1.8cm} >{\raggedright\arraybackslash}p{2.0cm} >{\raggedright\arraybackslash}p{2.2cm} X >{\raggedright\arraybackslash}p{1.6cm}}
\toprule
\textbf{Req.} & \textbf{Test ID} & \textbf{Method} & \textbf{Observed Result} & \textbf{Status}\\
\midrule
FRQ-1 & FRQ-1-SUBMIT & UI automation + DB check & Reimbursement requests were submitted successfully with required metadata and receipt links persisted. & Pass\\
FRQ-2 & FRQ-2-REVIEW & UI workflow + backend verification & Reviewer approval/rejection actions updated request state correctly and recorded reviewer decision details. & Pass\\
FRQ-3 & FRQ-3-STATUS & API + UI cross-check & Status values displayed in the dashboard matched API responses and underlying stored state. & Pass\\
FRQ-4 & FRQ-4-STORAGE & Storage/API verification & Uploaded receipts remained retrievable after submission and were protected by role-based access constraints. & Pass\\
FRQ-5 & FRQ-5-AUDIT & Automated log checks & Audit entries were generated for submission and decision events with actor identity and timestamps. & Pass\\
FRQ-6 & FRQ-3-STATUS + role checks & UI/API authorization checks & Access to reimbursement records followed role permissions for submitters, elevated club roles, and MES administrators. & Pass\\
\bottomrule
\end{tabularx}

\section{Nonfunctional Requirements Evaluation}

This section evaluates nonfunctional qualities from the SRS using the planned
test set \texttt{NFL-SAL-1}, \texttt{NFL-USAB-1}, \texttt{NFL-SEC-1}, and
\texttt{NFL-MNT-1}. The objective was to verify whether the system meets
quality expectations for usability, performance, security/privacy,
maintainability, and operational reliability.

\subsection{Usability}

Usability was assessed using task-based sessions aligned with the VnV Plan.
Participants completed representative actions (submit reimbursement,
review/approve, track status) and then provided structured feedback.

\textbf{Outcome:}
Users were able to complete core tasks without external assistance, and role
navigation was generally intuitive. Survey feedback indicated that form layout,
status visibility, and confirmation cues were understandable for first-time use.

\textbf{Assessment:} Pass.
		
\subsection{Performance}

Performance and latency were evaluated through staged load execution on core API
paths and common page loads, following \texttt{NFL-SAL-1}.

\textbf{Outcome:}
Observed response behavior remained within acceptable limits for expected usage,
and no stability failures were observed during concurrent request testing.
Upload and request/review interactions remained responsive under the tested
workload.

\textbf{Assessment:} Pass.

\subsection{Security and Privacy}

Security verification focused on role-based authorization, input validation, and
data protection controls from SRS categories \texttt{ACS}, \texttt{INT}, and
\texttt{PRI} as planned in \texttt{NFL-SEC-1}.

\textbf{Outcome:}
Unauthorized operations were denied, role boundaries were enforced at protected
routes, and sensitive reimbursement data remained scoped to authorized users.
Validation and sanitization checks reduced risk for malformed or malicious
inputs.

\textbf{Assessment:} Pass.

\subsection{Maintainability and Supportability}

Maintainability was evaluated using linting/format checks and documentation
review activities from \texttt{NFL-MNT-1}.

\textbf{Outcome:}
The codebase satisfied the configured static quality gates used during
verification. Repository documentation provides sufficient guidance for setup and
routine development workflows, supporting continued team maintenance.

\textbf{Assessment:} Pass with minor improvement opportunities for expanding
troubleshooting documentation and regression-test onboarding notes.

\subsection{Overall Nonfunctional Summary}

\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{2.8cm} >{\raggedright\arraybackslash}p{2.4cm} X >{\raggedright\arraybackslash}p{1.6cm}}
\toprule
\textbf{Quality Attribute} & \textbf{Primary Test ID(s)} & \textbf{Summary} & \textbf{Status}\\
\midrule
Usability/Accessibility & NFL-USAB-1 & Task completion and user feedback support ease-of-use objectives for intended roles. & Pass\\
Performance/Latency & NFL-SAL-1 & System remained responsive under representative concurrent activity and page/API load checks. & Pass\\
Security/Privacy & NFL-SEC-1 & Authorization boundaries and input protection checks behaved as required. & Pass\\
Maintainability/Supportability & NFL-MNT-1 & Static quality checks and documentation baseline support sustainable development. & Pass\\
\bottomrule
\end{tabularx}
	
\section{Comparison to Existing Implementation}	

This section will not be appropriate for every project.

\section{Unit Testing}

\section{Changes Due to Testing}

\wss{This section should highlight how feedback from the users and from 
the supervisor (when one exists) shaped the final product.  In particular 
the feedback from the Rev 0 demo to the supervisor (or to potential users) 
should be highlighted.}

\section{Automated Testing}
		
\section{Trace to Requirements}
		
\section{Trace to Modules}		

\section{Code Coverage Metrics}

\bibliographystyle{plainnat}
\nocite{*}
\bibliography{../../refs/References}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?

  \noindent\textbf{Justin response:} What went well while writing this
  deliverable was how our team took initiative and split work efficiently
  without heavy micromanagement. We were able to move quickly, keep momentum,
  and still align our writing style during review.

  \item What pain points did you experience during this deliverable, and how
    did you resolve them?

  \noindent\textbf{Justin response:} The main pain point was inconsistent
  understanding of some VnV expectations early on, especially around the level
  of detail for test case descriptions. We resolved this by discussing the
  rubric and template together, then standardizing our format before final
  edits.

  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?

  \noindent\textbf{Justin response:} The sections most influenced by
  client/proxy feedback were the usability and workflow validation parts, since
  they reflect how club members and finance reviewers actually use the system.
  Parts that were less directly influenced were technical verification details
  (for example, automation tooling and static analysis planning), because those
  were primarily based on engineering best practices and team implementation
  constraints.

  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)

  \noindent\textbf{Justin response:} The VnV Plan and actual VnV activities
  were mostly aligned, but we adjusted scope and sequencing as implementation
  realities became clearer. Some planned tests were deferred or simplified so we
  could prioritize high-risk flows first (submission, review, status, and access
  control). These changes occurred because of time constraints and evolving
  technical understanding during development. In future projects, I would still
  expect some deviations, but we can reduce them by planning explicit priority
  tiers (must-have, should-have, nice-to-have) from the beginning.
\end{enumerate}

\end{document}